Error Summary (teaching-v1.0)

### 2020-12-11 experiment-1/analysis/preprocessor/error_summary.Rmd
remove here()
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}
if (!require("here")) {install.packages("here"); require("here")}

# set working directory
here::i_am("error_summary.Rmd")

# function
source(here("function.R"))

# read a text file for ideal performance
dt_ideal <- read.table(here("ideal.txt"))
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
# 
dt_onset <- fread(file = here("filtered", "dt_correct_onset.txt"), sep = ",")
dt_offset <- fread(file = here("filtered", "dt_correct_offset.txt"), sep = ",")
error_onset <- fread(file = here("filtered", "error_onset.txt"), sep = ",")
error_offset <- fread(file = here("filtered", "error_offset.txt"), sep = ",")
```

@@

>>>>

```{r setup, include = FALSE}
# packages
# data manipulation
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
# plot
if (!require("ggplot2")) {install.packages("ggplot2"); require("ggplot2")}

# function
source("function.R")

# read a text file for ideal performance
dt_ideal <- read.table("ideal.txt")
colnames(dt_ideal) <- "Pitch"
dt_ideal$RowNr <- 1:nrow(dt_ideal)
setcolorder(dt_ideal, c(2, 1))
# 
dt_onset <- fread(file = "filtered/dt_correct_onset.txt", sep = ",")
dt_offset <- fread(file = "filtered/dt_correct_offset.txt", sep = ",")
error_onset <- fread(file = "filtered/error_onset.txt", sep = ",")
error_offset <- fread(file = "filtered/error_offset.txt", sep = ",")
```

@@

```{r export, include = FALSE}
knitr::purl("error_summary.Rmd")
```
